---
title: "mbruner3_Assign1"
author: "Mark Bruner"
date: "10/9/2020"
output:
  html_document: default
  pdf_document: default
---
```{r}
rm(list = ls())
```

```{r}
library(tidyverse)
Online_Retail <- read_csv("Online_Retail.csv", col_types = c("ccci?dcc"))
head(Online_Retail)
```
# NUMBER 1
```{r}
Online_Retail %>%
group_by(Country)  %>%
  tally(sort = TRUE) %>% summarise(Country, Counts = n, Percent = n/sum(n)*100) %>% filter(Percent > 1)
```
UK, Germany, France, and EIRE account for more than 1% of the total transactions in this dataset.

#NUMBER 2
```{r}
Online_Retail <- mutate(Online_Retail, TransactionValue = Quantity * UnitPrice)
head(Online_Retail)
```
# NUMBER 3
```{r}
Online_Retail %>%
group_by(Country) %>% 
  summarise(TransValueSum = sum(TransactionValue)) %>% filter(TransValueSum > 130000) %>% arrange(desc(TransValueSum))
```
UK, Netherlands, EIRE, Germany, France, and Australia are the countries where their sum is greater than 130,000 British Pound.

# Number 4 Intro
```{r}
Temp <- strptime(Online_Retail$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
head(Temp)
head(Online_Retail)
Online_Retail$New_Invoice_Date <- as.Date(Temp)
Online_Retail$Invoice_Day_Week <- weekdays(Online_Retail$New_Invoice_Date)
Online_Retail$New_Invoice_Hour <- as.numeric(format(Temp, "%H"))
Online_Retail$New_Invoice_Month <- as.numeric(format(Temp, "%m"))
head(Online_Retail)
```

Part a
```{r}
Online_Retail %>%  
  group_by(Invoice_Day_Week) %>% 
  tally(sort = TRUE) %>% 
  summarise(Invoice_Day_Week, TransactionCounts = n, Percent = n/sum(n)*100) %>% 
  arrange(desc(TransactionCounts))
```
Part b
```{r}
Online_Retail %>% 
  group_by(Invoice_Day_Week) %>% 
  summarise(TransValueSum = sum(TransactionValue)) %>%
  mutate(TransValuePercent = TransValueSum/sum(TransValueSum)) %>% 
  arrange(desc(TransValueSum))
```
Part c
```{r}
Online_Retail %>%
  group_by(New_Invoice_Month) %>% 
  summarise(TransValueSum = sum(TransactionValue)) %>% 
  mutate(TransValuePercent = TransValueSum/sum(TransValueSum)) %>% 
  arrange(desc(TransValuePercent))
```
Part d
```{r}
Online_Retail %>% 
  filter(Country == "Australia") %>% 
  group_by(InvoiceDate) %>% 
  tally(sort = TRUE) %>% 
  filter(n == max(n))
```
Part e
```{r}
Online_Retail %>% 
  group_by(New_Invoice_Hour) %>% 
  tally(sort = TRUE) %>% 
  filter(New_Invoice_Hour>= 7 & New_Invoice_Hour<=20) %>% 
  arrange(n) %>% 
  head(3)
```
The answer is the 19th and 20th since they are the 2nd and 3rd lowest values and then combined would be the lowest sum of two consecutive hours.

```{r}
Online_Retail %>%
  group_by(Country) %>%
  filter(Country == "Germany") %>% 
  group_by(New_Invoice_Month) %>% 
  summarise(TransValueSum = sum(TransactionValue)) -> Germany

hist(Germany$TransValueSum, border = "deepskyblue3", main = "Germany Transaction Value", xlab = "Transaction Value Sum per Month", ylab = "Frequency", col = "deepskyblue")

```
# Number 6
```{r}

Online_Retail %>%
  group_by(CustomerID) %>%
  tally(sort = TRUE) %>% 
  filter(!is.na(CustomerID)) %>% 
  filter(n==max(n))

```

# Number 7
```{r}
colMeans(is.na(Online_Retail))
```

# Number 8
```{r}
Online_Retail %>% 
  group_by(Country) %>% 
  summarise(CustomerID) %>% 
  filter(is.na(CustomerID)) %>% 
  tally(sort = TRUE) # Total "NA" by country.
```
# Number 9
```{r}
Online_Retail %>% # Creating a variable for the number of days between visits.
  select(CustomerID, New_Invoice_Date) %>% 
  group_by(CustomerID) %>% 
  distinct(New_Invoice_Date) %>% 
  arrange(desc(CustomerID)) %>% 
  mutate(DaysBetween = New_Invoice_Date - lag(New_Invoice_Date))-> CustDaysBtwVisit #Combined DaysBetween per CustomerID.  
 
CustDaysBtwVisit %>% 
   filter(!is.na(DaysBetween)) -> RetCustDaysBtwVisits # Separated "NA" from dataset.

mean(RetCustDaysBtwVisits$DaysBetween)
```
  The customers who did return had an average of 38.5 days between visits.

# Number 10
```{r}
Online_Retail %>% # Found the returns from France.
  group_by(Country) %>% 
  filter(Country == "France") %>% 
  select(Country, Quantity) %>% 
  filter(Quantity < 0) -> FrenchReturns

  Online_Retail %>%  # Found the purchases from France.
  group_by(Country) %>% 
  filter(Country == "France") %>% 
  select(Quantity, Country) %>% 
  filter(Quantity > 0) -> FrenchPurchases

FRReturns <- sum(FrenchReturns$Quantity) # calculated the quantity of returns from France.
FRTransactions <- sum(FrenchPurchases$Quantity) # calculated the quanity of purchased from France.

FRReturns/FRTransactions *100 # Using the above two numbers, I then calculated the return rate.
```
France has a 1.45% return rate.

# Number 11
```{r}
Online_Retail %>%
  group_by(StockCode) %>% 
  summarise(TransactionValueTot = sum(TransactionValue)) %>% 
  arrange(desc(TransactionValueTot)) %>% 
  filter(StockCode != "DOT") %>%  # Looks like this is postage for delivering products.
  filter(TransactionValueTot == max(TransactionValueTot))

Online_Retail %>% 
  group_by(StockCode) %>% 
  filter(StockCode == "22423") %>% 
  select(StockCode, Description) %>% 
  distinct(StockCode, Description) %>% 
  filter(Description == "REGENCY CAKESTAND 3 TIER")
```
# Number 12
```{r}
Online_Retail %>% 
  group_by(CustomerID) %>% 
  distinct(CustomerID) -> UniqueCustomers

  length(UniqueCustomers$CustomerID)
```
There are 4373 unique customers in this dataset.

  